TBD

### 2024-04-06 outputs/paper/paper.qmd
dataset changed, rearrange files

>>>>

library(maps)
library(dplyr)
library(readr)
library(viridis)
library(ggplot2)

# Generating fake data for average house prices for each US state
set.seed(42) # For reproducibility
states <- map_data("state")$region %>% unique()
average_house_prices <- runif(n = length(states), min = 100000, max = 700000)
state_average_prices <- data.frame(State = states, AverageHousePrice = average_house_prices)

# Getting map data
us_states_map <- map_data("state")

# Merging the map data with the fake average house prices
map_data_merged <- merge(us_states_map, state_average_prices, by.x = "region", by.y = "State")

# Creating the heatmap
ggplot() +
  geom_polygon(data = map_data_merged, aes(x = long, y = lat, group = group, fill = AverageHousePrice), color = "white") +
  coord_fixed(1.3) +
  viridis::scale_fill_viridis(name = "Avg House Price", option = "plasma") +
  theme_minimal() +
  labs(title = "Average House Price by State in the US (Fake Data)",
       subtitle = "Data: Generated",
       caption = "Visualization by Example") +
  theme(legend.position = "right")
